Synthesising Complex Termination Arguments

### 2014-06-03 papers/termination/paper.tex
Examples

@@

@@

>>>>

\lstset{language=c++}

@@

A program that does not terminate for integers, but does for bitvectors:
\begin{lstlisting}
while(x > 0)
  x++;
\end{lstlisting}

A program that terminates for integers, but does not for bitvectors:
\begin{lstlisting}
while (x > 0)
 x -= 2;
\end{lstlisting}

A program that does not terminate for reals, but does for floats:
\begin{lstlisting}
while (x > 0.0)
 x *= 0.5;
\end{lstlisting}

A program that terminates for reals, but does not for floats:
\begin{lstlisting}
while (x > 0.0)
 x -= 1.0;
\end{lstlisting}

A non-linear program with a linear ranking function:
\begin{lstlisting}
while (x > 0)
 x = (x - 1) & x;
\end{lstlisting}

A linear program with a non-linear ranking function:
\begin{lstlisting}
while (x != 0)
 x = -x / 2;
\end{lstlisting}

@@

We implemented our fully automatic program synthesis procedure in the \textsc{Kalashnikov} tool.
